---
title: "MycoBank Gap Report — `r params$taxon`"
subtitle: "MycoBank species missing from the Flora e Funga do Brasil checklist"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
author: "Generated by [fungaR](https://dboslab.github.io/fungaR-website/)"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    number_sections: false
    df_print: paged
    css: !expr system.file("rmd/funga_report.css", package = "fungaR")
params:
  data_path: NULL
  taxon: "TAXON"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  out.width = "100%"
)

library(DT)

# Load pre-computed analysis data
d <- readRDS(params$data_path)
taxon <- d$taxon
comma <- function(x) format(x, big.mark = ",", scientific = FALSE, trim = TRUE)
# Absolute path so the logo embeds correctly regardless of the working
# directory pandoc uses at render time (self-contained HTML needs a real,
# resolvable file path, not one relative to the output directory).
logo_path <- system.file("figures", "fungaR_hex_sticker.png", package = "fungaR")
```

<div style="float:right; margin-top:-80px; margin-left:15px;">
  <a href="https://dboslab.github.io/fungaR-website/" target="_blank">
    <img src="`r logo_path`"
         style="width:120px;transition:opacity 0.2s ease;"
         onmouseover="this.style.opacity='0.8'"
         onmouseout="this.style.opacity='1'"
         alt="fungaR package logo">
  </a>
</div>

---

## Overview

Species-level names classified by [MycoBank](https://www.mycobank.org) under
**`r taxon`** (`r d$rank`) were compared against the current
[Flora e Funga do Brasil (FFB)](https://floradobrasil.jbrj.gov.br/consulta/)
checklist to flag names that are not yet registered in FFB. Names are compared
by their *currently accepted* MycoBank name, so an obscure historical synonym
of a species FFB already lists under a different name is not flagged.

```{r kpi-boxes}
kpi_boxes <- list(
  htmltools::tags$div(
    class = "kpi-box kpi-gold",
    htmltools::tags$div(class = "kpi-value", comma(d$n_mycobank)),
    htmltools::tags$div(class = "kpi-label",
                        paste0("Species-level names in MycoBank for ", taxon))
  ),
  htmltools::tags$div(
    class = "kpi-box kpi-green",
    htmltools::tags$div(class = "kpi-value", comma(d$n_in_ffb)),
    htmltools::tags$div(class = "kpi-label", "Already registered in FFB")
  ),
  htmltools::tags$div(
    class = "kpi-box kpi-red",
    htmltools::tags$div(class = "kpi-value", comma(d$n_missing)),
    htmltools::tags$div(class = "kpi-label", "Missing from FFB")
  )
)

if (!is.null(d$n_with_evidence)) {
  kpi_boxes <- c(kpi_boxes, list(
    htmltools::tags$div(
      class = "kpi-box kpi-amber",
      htmltools::tags$div(class = "kpi-value", comma(d$n_with_evidence)),
      htmltools::tags$div(class = "kpi-label",
                          "Missing species with Brazil occurrence evidence")
    )
  ))
}

do.call(htmltools::tags$div, c(class = "kpi-row", kpi_boxes))
```

---

## Missing Species by Family

```{r table-family}
fam <- d$family_gap

if (is.null(fam) || nrow(fam) == 0) {
  htmltools::p("No family information available.",
              style = "color: #6c757d; font-style: italic;")
} else {
  DT::datatable(
    fam,
    colnames = c("Family", "Missing species"),
    rownames = FALSE,
    caption = htmltools::tags$caption(
      style = "caption-side: top; text-align: left; font-weight: bold;",
      "Table 1. Families contributing the most MycoBank species missing from FFB."
    ),
    options = list(pageLength = 10, dom = "ftp",
                  order = list(list(1, "desc")))
  ) %>%
    DT::formatStyle("n_missing",
                    background = DT::styleColorBar(fam$n_missing, "#FCF3DE"),
                    backgroundSize = "98% 88%",
                    backgroundRepeat = "no-repeat",
                    backgroundPosition = "center")
}
```

---

## Complete List of Missing Species

The table below lists all `r comma(d$n_missing)` species-level MycoBank names
for **`r taxon`** that are not currently in FFB, including each name's
original MycoBank page. Use the column filters to narrow the list, and the
buttons above the table to copy or download it as CSV/Excel.

```{r table-missing}
tbl <- d$result

if ("MycoBank_URL" %in% names(tbl)) {
  tbl$MycoBank_URL <- ifelse(
    !is.na(tbl$MycoBank_URL) & nzchar(tbl$MycoBank_URL),
    paste0('<a href="', tbl$MycoBank_URL, '" target="_blank">MycoBank page</a>'),
    ""
  )
}

DT::datatable(
  tbl,
  rownames = FALSE,
  escape = FALSE,
  filter = list(position = "top", clear = TRUE, plain = FALSE),
  extensions = c("Buttons"),
  caption = htmltools::tags$caption(
    style = "caption-side: top; text-align: left; font-weight: bold;",
    paste0("Table 2. All ", comma(d$n_missing),
           " MycoBank species missing from FFB for ", taxon, ".")
  ),
  options = list(
    pageLength = 20,
    dom = "Bfrtip",
    buttons = c("copy", "csv", "excel"),
    scrollX = TRUE,
    search = list(regex = TRUE, caseInsensitive = TRUE),
    lengthMenu = list(c(10, 20, 50, 100, -1),
                      c("10", "20", "50", "100", "All"))
  )
)
```

---

<footer style="text-align:center; color:#adb5bd; font-size:0.85em; margin-top:2em; padding-top:1em; border-top:1px solid #dee2e6;">
Analysis produced by <strong>fungaR</strong> &bull;
Flora e Funga do Brasil &bull;
MycoBank &bull;
`r format(Sys.Date(), "%Y")`
</footer>
