---
title: "Distribution Gap Report — `r params$taxon`"
subtitle: "Brazilian states with occurrence evidence not yet listed in the FFB distribution"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
author: "Generated by [fungaR](https://dboslab.github.io/fungaR-website/)"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    number_sections: false
    df_print: paged
    css: !expr system.file("rmd/funga_report.css", package = "fungaR")
params:
  data_path: NULL
  taxon: "TAXON"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  out.width = "100%"
)

library(DT)

# Load pre-computed analysis data
d <- readRDS(params$data_path)
taxon <- d$taxon
comma <- function(x) format(x, big.mark = ",", scientific = FALSE, trim = TRUE)
# Absolute path so the logo embeds correctly regardless of the working
# directory pandoc uses at render time (self-contained HTML needs a real,
# resolvable file path, not one relative to the output directory).
logo_path <- system.file("figures", "fungaR_hex_sticker.png", package = "fungaR")
```

<div style="float:right; margin-top:-80px; margin-left:15px;">
  <a href="https://dboslab.github.io/fungaR-website/" target="_blank">
    <img src="`r logo_path`"
         style="width:120px;transition:opacity 0.2s ease;"
         onmouseover="this.style.opacity='0.8'"
         onmouseout="this.style.opacity='1'"
         alt="fungaR package logo">
  </a>
</div>

---

## Overview

Brazilian states with occurrence evidence for **`r taxon`** from GBIF,
speciesLink, and/or the Reflora Virtual Herbarium (REFLORA) were compared
against the states officially listed for this taxon in the
[Flora e Funga do Brasil (FFB)](https://floradobrasil.jbrj.gov.br/consulta/)
distribution, to flag candidate new state records.

```{r kpi-boxes}
htmltools::tags$div(
  class = "kpi-row",
  htmltools::tags$div(
    class = "kpi-box kpi-green",
    htmltools::tags$div(class = "kpi-value", comma(d$n_in_ffb)),
    htmltools::tags$div(class = "kpi-label", "States already in FFB distribution")
  ),
  htmltools::tags$div(
    class = "kpi-box kpi-gold",
    htmltools::tags$div(class = "kpi-value", comma(d$n_states_total)),
    htmltools::tags$div(class = "kpi-label", "States with any occurrence evidence")
  ),
  htmltools::tags$div(
    class = "kpi-box kpi-red",
    htmltools::tags$div(class = "kpi-value", comma(d$n_new_candidates)),
    htmltools::tags$div(class = "kpi-label", "New state record candidates")
  )
)
```

---

## Evidence by Source

```{r table-source}
src <- d$source_summary

if (is.null(src) || nrow(src) == 0) {
  htmltools::p("No source summary available.",
              style = "color: #6c757d; font-style: italic;")
} else {
  DT::datatable(
    src,
    colnames = c("Source", "States with evidence"),
    rownames = FALSE,
    caption = htmltools::tags$caption(
      style = "caption-side: top; text-align: left; font-weight: bold;",
      "Table 1. Number of states with occurrence evidence, by source."
    ),
    options = list(pageLength = 5, dom = "t")
  ) %>%
    DT::formatStyle("n_states",
                    background = DT::styleColorBar(src$n_states, "#FCF3DE"),
                    backgroundSize = "98% 88%",
                    backgroundRepeat = "no-repeat",
                    backgroundPosition = "center")
}
```

---

## Complete State-by-State Table

The table below lists every Brazilian state with any occurrence evidence for
**`r taxon`**, flagging `New_state_record_candidate = TRUE` for states with
external evidence not yet in FFB's official distribution. Use the column
filters to narrow the list, and the buttons above the table to copy or
download it as CSV/Excel.

```{r table-states}
tbl <- d$result

DT::datatable(
  tbl,
  rownames = FALSE,
  filter = list(position = "top", clear = TRUE, plain = FALSE),
  extensions = c("Buttons"),
  caption = htmltools::tags$caption(
    style = "caption-side: top; text-align: left; font-weight: bold;",
    paste0("Table 2. All ", comma(nrow(tbl)),
           " state(s) with occurrence evidence for ", taxon, ".")
  ),
  options = list(
    pageLength = 20,
    dom = "Bfrtip",
    buttons = c("copy", "csv", "excel"),
    scrollX = TRUE,
    search = list(regex = TRUE, caseInsensitive = TRUE),
    lengthMenu = list(c(10, 20, 50, 100, -1),
                      c("10", "20", "50", "100", "All"))
  )
) %>%
  DT::formatStyle(
    "New_state_record_candidate",
    backgroundColor = DT::styleEqual(c(TRUE, FALSE), c("#fde8ea", "#EEF6EC"))
  )
```

---

## Individual Records for the New State Candidates

Unlike the state-level table above, this table lists the actual **individual**
occurrence records (not aggregated by state) found in Brazilian states that are
not yet in FFB's official distribution for **`r taxon`** - each one linking out
to the specific record in its source database (GBIF occurrence page, or the
REFLORA specimen page).

```{r table-records}
recs <- d$records_detail

if (is.null(recs) || nrow(recs) == 0) {
  htmltools::p(
    "No individual records were retrieved for the new-state-record candidates ",
    "(GBIF/REFLORA may not have been among the requested 'sources', or no ",
    "records were found).",
    style = "color: #6c757d; font-style: italic;"
  )
} else {
  if ("RecordLink" %in% names(recs)) {
    recs$RecordLink <- ifelse(
      !is.na(recs$RecordLink) & nzchar(recs$RecordLink),
      paste0('<a href="', recs$RecordLink, '" target="_blank">', recs$RecordLink, '</a>'),
      ""
    )
  }

  DT::datatable(
    recs,
    rownames = FALSE,
    escape = FALSE,
    filter = list(position = "top", clear = TRUE, plain = FALSE),
    extensions = c("Buttons"),
    caption = htmltools::tags$caption(
      style = "caption-side: top; text-align: left; font-weight: bold;",
      paste0("Table 3. All ", comma(nrow(recs)),
             " individual record(s) found in new-state-record candidates for ",
             taxon, ".")
    ),
    options = list(
      pageLength = 20,
      dom = "Bfrtip",
      buttons = c("copy", "csv", "excel"),
      scrollX = TRUE,
      search = list(regex = TRUE, caseInsensitive = TRUE),
      lengthMenu = list(c(10, 20, 50, 100, -1),
                        c("10", "20", "50", "100", "All"))
    )
  )
}
```

---

<footer style="text-align:center; color:#adb5bd; font-size:0.85em; margin-top:2em; padding-top:1em; border-top:1px solid #dee2e6;">
Analysis produced by <strong>fungaR</strong> &bull;
Flora e Funga do Brasil &bull;
GBIF &bull; speciesLink &bull; REFLORA &bull;
`r format(Sys.Date(), "%Y")`
</footer>
