---
title: "Index Fungorum Gap Report — `r params$taxon`"
subtitle: "Index Fungorum species with Brazil evidence missing from the Flora e Funga do Brasil checklist"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
author: "Generated by [fungaR](https://dboslab.github.io/fungaR-website/)"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    number_sections: false
    df_print: paged
    css: !expr system.file("rmd/funga_report.css", package = "fungaR")
params:
  data_path: NULL
  taxon: "TAXON"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  out.width = "100%"
)

library(DT)

# Load pre-computed analysis data
d <- readRDS(params$data_path)
taxon <- d$taxon
comma <- function(x) format(x, big.mark = ",", scientific = FALSE, trim = TRUE)
logo_path <- system.file("figures", "fungaR_hex_sticker.png", package = "fungaR")
```

<div style="float:right; margin-top:-80px; margin-left:15px;">
  <a href="https://dboslab.github.io/fungaR-website/" target="_blank">
    <img src="`r logo_path`"
         style="width:120px;transition:opacity 0.2s ease;"
         onmouseover="this.style.opacity='0.8'"
         onmouseout="this.style.opacity='1'"
         alt="fungaR package logo">
  </a>
</div>

---

## Overview

Species-level names classified by [Index Fungorum](https://www.speciesfungorum.org) under
**`r taxon`** (genus) were compared against the current
[Flora e Funga do Brasil (FFB)](https://floradobrasil.jbrj.gov.br/consulta/)
checklist. Names are compared by their *currently accepted* Index Fungorum name (as well
as their raw name, since the two databases occasionally disagree on which genus a name
currently belongs to), so an obscure historical synonym of a species FFB already lists
under a different name is not flagged.

`r if (isTRUE(d$brazil_filtered)) "This report is filtered to only the names whose own Index Fungorum reported locality mentions Brazil (the country or any Brazilian state) - i.e. species Index Fungorum itself places in the country but that FFB is still missing, not a general diff of the two databases." else "Locality was not used to filter these results; the table below lists every Index Fungorum name missing from FFB regardless of locality."`

```{r kpi-boxes}
kpi_boxes <- list(
  htmltools::tags$div(
    class = "kpi-box kpi-gold",
    htmltools::tags$div(class = "kpi-value", comma(d$n_fungorum)),
    htmltools::tags$div(class = "kpi-label",
                        paste0("Species-level names in Index Fungorum for ", taxon))
  ),
  htmltools::tags$div(
    class = "kpi-box kpi-green",
    htmltools::tags$div(class = "kpi-value", comma(d$n_in_ffb)),
    htmltools::tags$div(class = "kpi-label", "Already registered in FFB")
  ),
  htmltools::tags$div(
    class = "kpi-box kpi-red",
    htmltools::tags$div(class = "kpi-value", comma(d$n_missing)),
    htmltools::tags$div(class = "kpi-label",
                        if (isTRUE(d$brazil_filtered)) {
                          "Missing from FFB with Index Fungorum Brazil evidence"
                        } else {
                          "Missing from FFB"
                        })
  )
)

if (isTRUE(d$brazil_filtered)) {
  kpi_boxes <- c(kpi_boxes, list(
    htmltools::tags$div(
      class = "kpi-box kpi-amber",
      htmltools::tags$div(class = "kpi-value", comma(d$n_missing_any_locality)),
      htmltools::tags$div(class = "kpi-label", "Missing from FFB (any locality, for context)")
    )
  ))
}

do.call(htmltools::tags$div, c(class = "kpi-row", kpi_boxes))
```

---

## `r if (isTRUE(d$brazil_filtered)) "Species with Index Fungorum Brazil Evidence Missing from FFB" else "Complete List of Missing Species"`

`r if (isTRUE(d$brazil_filtered)) paste0("The table below lists all ", comma(d$n_missing), " species-level Index Fungorum names for **", taxon, "** whose own reported locality mentions Brazil, but that are not currently in FFB - including each name's original Species Fungorum page. This is not a general diff of the two databases: names Index Fungorum places outside Brazil are excluded.") else paste0("The table below lists all ", comma(d$n_missing), " species-level Index Fungorum names for **", taxon, "** that are not currently in FFB, including each name's original Species Fungorum page.")` Use the column filters to narrow the list, and the
buttons above the table to copy or download it as CSV/Excel.

```{r table-missing}
tbl <- d$result

if ("Fungorum_URL" %in% names(tbl)) {
  tbl$Fungorum_URL <- ifelse(
    !is.na(tbl$Fungorum_URL) & nzchar(tbl$Fungorum_URL),
    paste0('<a href="', tbl$Fungorum_URL, '" target="_blank">', tbl$Fungorum_URL, '</a>'),
    ""
  )
}

DT::datatable(
  tbl,
  rownames = FALSE,
  escape = FALSE,
  filter = list(position = "top", clear = TRUE, plain = FALSE),
  extensions = c("Buttons"),
  caption = htmltools::tags$caption(
    style = "caption-side: top; text-align: left; font-weight: bold;",
    paste0("Table 1. All ", comma(d$n_missing),
           " Index Fungorum species missing from FFB for ", taxon,
           if (isTRUE(d$brazil_filtered)) " with Index Fungorum Brazil evidence" else "", ".")
  ),
  options = list(
    pageLength = 20,
    dom = "Bfrtip",
    buttons = c("copy", "csv", "excel"),
    scrollX = TRUE,
    search = list(regex = TRUE, caseInsensitive = TRUE),
    lengthMenu = list(c(10, 20, 50, 100, -1),
                      c("10", "20", "50", "100", "All"))
  )
)
```

---

<footer style="text-align:center; color:#adb5bd; font-size:0.85em; margin-top:2em; padding-top:1em; border-top:1px solid #dee2e6;">
Analysis produced by <strong>fungaR</strong> &bull;
Flora e Funga do Brasil &bull;
Index Fungorum &bull;
`r format(Sys.Date(), "%Y")`
</footer>
