---
title: "Index Fungorum Records Report — `r params$taxon`"
subtitle: "Index Fungorum records with Brazil evidence"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
author: "Generated by [fungaR](https://dboslab.github.io/fungaR-website/)"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    number_sections: false
    df_print: paged
    css: !expr system.file("rmd/funga_report.css", package = "fungaR")
params:
  data_path: NULL
  taxon: "TAXON"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  out.width = "100%"
)

library(DT)

# Load pre-computed analysis data
d <- readRDS(params$data_path)
taxon <- d$taxon
comma <- function(x) format(x, big.mark = ",", scientific = FALSE, trim = TRUE)
logo_path <- system.file("figures", "fungaR_hex_sticker.png", package = "fungaR")
```

<div style="float:right; margin-top:-80px; margin-left:15px;">
  <a href="https://dboslab.github.io/fungaR-website/" target="_blank">
    <img src="`r logo_path`"
         style="width:120px;transition:opacity 0.2s ease;"
         onmouseover="this.style.opacity='0.8'"
         onmouseout="this.style.opacity='1'"
         alt="fungaR package logo">
  </a>
</div>

---

## Overview

This report retrieves every name classified by [Index Fungorum](https://www.speciesfungorum.org)
matching **`r taxon`** (`r d$rank`). This is a retrieval report, not a comparison against
[Flora e Funga do Brasil (FFB)](https://floradobrasil.jbrj.gov.br/consulta/): it does not
check whether these names are already registered in FFB.

`r if (isTRUE(d$brazil_filtered)) "This report is filtered to only the names whose own Index Fungorum reported locality mentions Brazil (the country or any Brazilian state) - i.e. records Index Fungorum itself places in the country." else "Locality was not used to filter these results; the table below lists every matching Index Fungorum name regardless of locality."`

```{r kpi-boxes}
kpi_boxes <- list(
  htmltools::tags$div(
    class = "kpi-box kpi-gold",
    htmltools::tags$div(class = "kpi-value", comma(d$n_fungorum)),
    htmltools::tags$div(class = "kpi-label",
                        paste0("Matching Index Fungorum name(s) for ", taxon))
  ),
  htmltools::tags$div(
    class = "kpi-box kpi-red",
    htmltools::tags$div(class = "kpi-value", comma(d$n_records)),
    htmltools::tags$div(class = "kpi-label",
                        if (isTRUE(d$brazil_filtered)) {
                          "Records with Index Fungorum Brazil evidence"
                        } else {
                          "Records retrieved"
                        })
  )
)

do.call(htmltools::tags$div, c(class = "kpi-row", kpi_boxes))
```

---

## `r if (isTRUE(d$brazil_filtered)) "Records with Index Fungorum Brazil Evidence" else "Complete List of Matching Records"`

`r if (isTRUE(d$brazil_filtered)) paste0("The table below lists all ", comma(d$n_records), " Index Fungorum name(s) for **", taxon, "** whose own reported locality mentions Brazil, including each name's original Species Fungorum page.") else paste0("The table below lists all ", comma(d$n_records), " Index Fungorum name(s) for **", taxon, "**, including each name's original Species Fungorum page.")` Use the column filters to narrow the list, and the
buttons above the table to copy or download it as CSV/Excel.

```{r table-records}
tbl <- d$result

if ("Fungorum_URL" %in% names(tbl)) {
  tbl$Fungorum_URL <- ifelse(
    !is.na(tbl$Fungorum_URL) & nzchar(tbl$Fungorum_URL),
    paste0('<a href="', tbl$Fungorum_URL, '" target="_blank">', tbl$Fungorum_URL, '</a>'),
    ""
  )
}

DT::datatable(
  tbl,
  rownames = FALSE,
  escape = FALSE,
  filter = list(position = "top", clear = TRUE, plain = FALSE),
  extensions = c("Buttons"),
  caption = htmltools::tags$caption(
    style = "caption-side: top; text-align: left; font-weight: bold;",
    paste0("Table 1. All ", comma(d$n_records),
           " Index Fungorum record(s) for ", taxon,
           if (isTRUE(d$brazil_filtered)) " with Index Fungorum Brazil evidence" else "", ".")
  ),
  options = list(
    pageLength = 20,
    dom = "Bfrtip",
    buttons = c("copy", "csv", "excel"),
    scrollX = TRUE,
    search = list(regex = TRUE, caseInsensitive = TRUE),
    lengthMenu = list(c(10, 20, 50, 100, -1),
                      c("10", "20", "50", "100", "All"))
  )
)
```

---

<footer style="text-align:center; color:#adb5bd; font-size:0.85em; margin-top:2em; padding-top:1em; border-top:1px solid #dee2e6;">
Analysis produced by <strong>fungaR</strong> &bull;
Flora e Funga do Brasil &bull;
Index Fungorum &bull;
`r format(Sys.Date(), "%Y")`
</footer>
